\input{../../assignment-header}

%========================================================================
\title{Assignment 10:  Hermite--Simpson Direct Collocation}
\date{Assigned:  April 6  ---  Due:  April 13 at 11:55pm}
\author{Optimal Control for Robotics}
%========================================================================
\begin{document}
\maketitle
%=================================================

\section*{Introduction}

In this assignment you will use the Hermtie--Simpson method for direct collocation
to compute the minimal-torque swing-up for a simple pendulum,
and the minimal-thrust flip maneuver for a planar quadrotor model.

\section*{Implementation Details}

\par There are two formulations of the Hermite--Simpson direct collocation
technique: separated and compressed. In the separated form, the state at the
midpoint of each segment is a decision variable, while in the compressed form
the state at each midpoint is explicitly computed on each iteration.
For this assignment please use the separated form.

\par This asignment is intentionally very similar to HW 09, with the
only difference being the collocation method.
You to start with your solution for HW 09, and then modify it to use the
Hermite--Simpson method instead of the trapezoid method.
You may choose instead to start with the solution to HW 09,
although you should make a note in the code that indicates this.

\par Hermite--Simpson direct collocation uses a cubic spline for the state and
a quadratic spline for the control. I suggest that you use the spline utilities
in the code library for the course to generate these splines, although you are
welcome to use you own implementation if desired.

\par I've included the solution in p-code form so that you can check your
implementation.

\section*{Deliverables}

Implement the function \texttt{dirColBvpHermiteSimpson.m} using the template provided.

%=================================================
\end{document}
