\section{Problem Statement}
\label{sec:ProblemStatement}

Simply put: fit a smooth function through a sequence of data points,
\textit{e.g.} Figure \ref{fig:DataFittingExampleFigure}. \\
More precisely:
\begin{itemize}
  \setlength\itemsep{0em}
  \item \textbf{Given:} a time-stamped set of points in space.
  \item \textbf{Find:} a smooth vector function.
  \item \textbf{Minimize:} integral of curvature-rate-squared and sum or squared-error.
  \item \textbf{Subject to:} value, slope, and curvature at the boundaries.
\end{itemize}

\par
We will use $\bm{x}(t)$ to represent value as a function of time.
The data set is $\{t_i, \bar{\bm{x}}_i\}$, which gives measured value at each time stamp.
The time-domain of the data set is $[0, T]$.

\subsection{Objective Function}

The objective function is a weighted combination of two terms.
The first is the sum of the squared-error between the candidate vector function and the points in the data set.
The second is a smoothing-term, minimizing the integral of the third derivative of the function.

\begin{equation}
  \bm{J}\big(\bm{x}(t)\big) \; =   \;
    \frac{T}{N}  \sum_{i=0}^N \big( \bm{x}(t_i) - \bar{\bm{x}}_i \big)^2
     \; +   \; \alpha \! \int_0^T \! \dddot{\bm{x}}^2(t) \, dt
  \label{eqn:continuousObjectiveFunction}
\end{equation}

\subsection{Constraints}

The vector function $\bm{x}(t)$ must be smooth: continuous value, slope, and curvature.
\begin{equation}
  \bm{x}(t) \in \mathcal{C}^2
\end{equation}

We also require that the value, slope, and curvature be prescribed at the initial and final times.
In practice these boundary constraints can be dropped if not required by the end-user.

\begin{align}
  \bm{x}(0) = \bm{x}_0  & \quad &  \bm{x}(T) = \bm{x}_T \\
  \dot{\bm{x}}(0) = \dot{\bm{x}}_0  & \quad & \dot{\bm{x}}(T) = \dot{\bm{x}}_T \\
  \ddot{\bm{x}}(0) = \ddot{\bm{x}}_0  & \quad & \ddot{\bm{x}}(T) = \ddot{\bm{x}}_T
\end{align}
